---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# smartsheetr

<!-- badges: start -->
<!-- badges: end -->

smartsheetr is an extensible [smartsheet](https://www.smartsheet.com/) API client. It utilizes the API to push/pull data frames as smartsheet documents.

## Installation

You can install the development version of smartsheetr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cole-johanson/smartsheetr")
```

You will also need to [generate a smartsheet API key](https://help.smartsheet.com/articles/2482389-generate-API-key) and then add it as a global enviroment variable:
``` r
Sys.setenv("SMARTSHEET_API_TOKEN" = <your token>)
```

## Example

Upload a sample data frame, and read it back into R:

```{r}
ss_mtcars_resp = smartsheetr::ss_write_sheet("mtcars", mtcars)
ss_mtcars_sheetid = smartsheetr::ss_response_parse(ss_mtcars_resp)$content$result[[1]]$sheetId
smartsheetr::ss_get_sheets() |> dplyr::filter(name == 'mtcars')
smartsheetr::ss_read_sheet(ss_mtcars_sheetid)
```

